\cvsection{Experience}
\begin{cventries}
	\cventry
		{TÜBİTAK}
		{Scholarship Student}
		{Muğla, TURKEY}
		{October 2016 - May 2017}
		{
			\begin{cvitems}
				\item {Learnt and Practiced Ruby, Ruby on Rails Application Development.}
				\item {Gained minor knowledge about LDAP Management (FreeIPA).}
				\item {Gained knowledge about web2py Project deployment, Ruby on Rails Project deployment}
				\item {Wrote some script for automate works. e.g: Auto user creation for LDAP, text-base scripting}
				\item {Gained knowledge about PXI Boot, Clonezilla}
				\item {Gained knowledge about docker as beginner level.}
			\end{cvitems}
		}
	\cventry
		{Türk Telekom Doğu-I Bölge Müdürlüğü}
		{Internship}
		{Erzurum, TURKEY}
		{June 2016 - August 2016}
		{
			\begin{cvitems}
				\item {Learnt Android Mobile Application Development, Application Lifecycle.}
				\item {Practiced and improved Java knowledge.}
				\item {Some application development for Android.}
				\item {Scripting practice. e.g: auto change version for all project}
			\end{cvitems}
		}
	\cventry
		{Muğla Sıtkı Koçman University, Computer Engineering Department}
		{Part-time}
		{Muğla, TURKEY}
		{October 2015 - June 2016}
		{Learnt scripting for installing requirement}
	\cventry
		{MSKU Computer Engineering Department - Asst. İzzet PEMBECİ}
		{Internship}
		{Muğla, TURKEY}
		{July 2015 - September 2015}
		{
		  \begin{cvitems}
			\item {Implemented a board game called Tally-Ho! in Ractive.js (Javascript Framework).}
			\item {Re-Implemented a library automation system with Laravel (which was implemented in pure PHP in previous semester).}
			\item {Tally-Ho!: https://github.com/mkocaker06/Tally-Ho}
		  \end{cvitems}
		}

\end{cventries}
