\cvsection{Projects}
\begin{cventries}
    \cventry
        {Member - Senior Design Project}
        {Rate'Mall}
        {}
        {October 2016 - May 2017}
        {
            \begin{cvitems}
                \item {Implementation: Django(Python), PostgreSQL}
            \end{cvitems}
        }

    \cventry
        {Member - Introduction to Bioinformatics Course Project}
        {Finding pathways for a given metabolite}
        {}
        {October 2016 - December 2016}
        {
            \begin{cvitems}
                \item {Gained knowledge about Bioinformatics' sources like KEGG, CheBI, WikiPathways, PubChem etc.}
                \item {Implementation: Python}
                \item {Source Code: https://github.com/mkocaker06/finding-pathways-for-metabolite}
            \end{cvitems}
        }

    \cventry
        {Information Retrieval Systems Course Project}
        {MOsTearch}
        {}
        {February 2016 - June 2016}
        {
            \begin{cvitems}
                \item {Gained knowledge about Solr.}
                \item {Used web2py for creating the search engine's UI.}
                \item {Implementation: web2py(Python), Solr}
            \end{cvitems}
        }

    \cventry
        {Member - GUI Programming Course Project}
        {League of Legends' Helper Desktop Application}
        {}
        {October 2015 - December 2015}
        {
            \begin{cvitems}
                \item {Gained knowledge about GUI design principles and heuristics.}
                \item {Learned Prototyping with Balsamiq Mockup.}
                \item {Implementation: C\#}
                \item {Source Code: https://github.com/erenvural/lol-helper}
            \end{cvitems}
        }

    \cventry
        {Member - Web Programming and Development Course Project}
        {League of Legends' Helper Website}
        {}
        {October 2015 - December 2015}
        {
            \begin{cvitems}
                \item {Gained knowledge about MVC and web-based application technologies.}
                \item {Implementation: Web2py (Python Framework)}
            \end{cvitems}
        }

    \cventry
        {Member - during internship}
        {Tally Ho! Game}
        {}
        {July 2015 - September 2015}
        {
            \begin{cvitems}
                \item {Gained a skill works as a team.}
                \item {Database from DBMS course}
                \item {Implementation: Ractive.JS and HTML \& CSS} 
                \item {Source Code: https://github.com/mkocaker06/Tally-Ho} 
            \end{cvitems}
        }

    \cventry
        {Member}
        {MSKU Sıtkı Koçman School of Foreign Languages Library Automation System}
        {}
        {March 2015 - July 2015}
        {
            \begin{cvitems}
                \item {Gained a skill works as a team.}
                \item {Database from DBMS course}
                \item {First implementation: pure PHP}
                \item {Re-implementation: Laravel}
            \end{cvitems}
        }

    \cventry
        {Member - DBMS Course Project}
        {MSKU Sıtkı Koçman School of Foreign Languages' Library Database}
        {}
        {February 2015 - May 2015}
        {
            \begin{cvitems}
                \item {Gained designing an Entity-Relationship(ER) Diagrams}
                \item {Learned Relational Algebra}
                \item {MySQL Workbench and phpmyadmin were used}
                \item {MySQL was used as database engine.}
            \end{cvitems}
        }

\end{cventries}
